Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-20 latex/article.tex

\noindent\textbf{Contributions}\quad In this work, we propose a
framework to perform interactive visualization of complex 3D digital
structures combined with a dynamic curvature tensor estimation. More
precisely, we define a fully data parallel process on GPU hardware to
both efficiently extract adaptive isosurface and compute per vertex
curvature tensor using Integral Invariants estimators. Hence, this
system allows us to visualize curvature tensor in realtime on large
dynamic objects. Our approach combines a GPU implementation of
pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of
integral invariant curvature estimations.

@@

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widelyo investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was developed to visualize in real-time static or near static data and
present a complex CPU implementation.  In this paper we propose a GPU
pipeline inspired from this method.  It leaves the CPU free for other
tasks and avoids synchronisation with the GPU.  Our high framerate
also allows this method to run in real-time on fully dynamic data.
The triangulation is controlled by a GPU LoD criterion that ensures
that triangles project onto more than one pixel, thus removing
geometrical aliasing.

@@

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to refine cells
within the camera frustrum. When rendering a mesh, a key stage is the
rasterization which digitizes triangles projected onto the
screen. As a consequence, having several triangles whose projections
lie inside the same pixel is something we should prevent. Hence,
distance criterion can be set in order to both control the geometrical
approximation and to ensure that cells project onto more than one
pixel. This does not prevent all triangles within such cells to be
projected into more than one pixel but gives us a fast criterion to
decide if a cell should be split or not.  Figure \ref{fig_lod_octree}
illustrates the level of details (LoD for short criterion) we
use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
angle, an object at distance $d$ from the camera with diameter greater than
 $2\cdot d\cdot\tan(\alpha)$
 is projected into more than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
criterion is based on the ratio (\emph{visibility ratio} in the
following)between the cell diameter $l(c)$ (power of 2 depending on
the depth), and
$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
split and merge decision are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ratio lower than $k$\;
\item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=4cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=4cm]{viewlod2_small}~~~~~
    \includegraphics[width=3.5cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

@@

>>>>

\noindent\textbf{Contributions}\quad In this work, we propose a
framework to perform interactive visualization of complex 3D digital
structures combined with a dynamic curvature tensor estimation. More
precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
both efficiently extract adaptive isosurface and compute per vertex
curvature tensor using Integral Invariants estimators. Hence, this
system allows us to visualize curvature tensor in realtime on large
dynamic objects. Our approach combines a GPU implementation of
pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of
integral invariant curvature estimations.

@@

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was developed to visualize in real-time static or near static data and
present a complex CPU implementation.  In this paper we propose a GPU
pipeline inspired from this method.  It leaves the CPU free for other
tasks and avoids synchronisation with the GPU.  Our high framerate
also allows this method to run in real-time on fully dynamic data.
The triangulation is controlled by a GPU LoD criterion that ensures
that triangles project onto more than one pixel, thus removing
geometrical aliasing.

@@

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to refine cells
within the camera frustrum. When rendering a mesh, a key stage is the
rasterization which digitizes triangles projected onto the
screen. As a consequence, having several triangles whose projections
lie inside the same pixel is something we should prevent. Hence,
distance criterion can be set in order to both control the geometrical
approximation and to ensure that cells project onto more than one
pixel. This does not prevent all triangles within such cells to be
projected into more than one pixel but gives us a fast criterion to
decide if a cell should be split or not.  Figure \ref{fig_lod_octree}
illustrates the level of details (LoD for short) criterion we
use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
angle, an object at distance $d$ from the camera with diameter greater than
 $2\cdot d\cdot\tan(\alpha)$
 is projected into more than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
criterion is based on the ratio (\emph{visibility ratio} in the
following)between the cell diameter $l(c)$ (power of 2 depending on
the depth), and
$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
split and merge decision are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ratio lower than $k$\;
\item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=4cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=4cm]{viewlod2_small}~~~~~
    \includegraphics[width=3.5cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figs/approx}
  \end{center}
  \caption{BALBLABLABLA.}
  \label{fig:approx}
\end{figure}
